---
title             : "Individual Differences in Congruency Effects"
shorttitle        : "My short title goes here"

author: 
  - name: Merle-Marie Pittelkow
    affiliation: "1"
    corresponding: yes    # Define only one corresponding author
    email: m.pittelkow@rug.nl
    address: Department of Psychology, University of Groningen
  - name: Annika Stump
    affiliation: "2"
  - name: Jasmine Muradchanian
    affiliation: "1"

affiliation       :
  - id: 1
    institution: University of Groningen
  - id: 2
    institution: University of Heidelberg



author_note       : "This paper was written as part of an open science class"

abstract          : >
  "Here"
  
keywords          : "are just words"

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no


class             : "man"

output            : papaja::apa6_pdf
---


# Background

Visual illusions are quite fun for humans. Be it to fool other or to scratch one's head. 
As part of the Transparent Open Science IOPS workshop by Jeff Rouder.


# Method
The nine participants completed an online visual task. Two dots were presented each at one side on the screen.


# Results

```{r}
dat=read.csv(url('https://raw.githubusercontent.com/PerceptionCognitionLab/data3/master/brightCompare1/data'),header=TRUE)
```


```{r acc}
m=tapply(dat$correct,list(dat$targLevel,dat$backLevel),mean)
```

```{r res,fig.cap="My Results"}
matplot(1:2,m,typ='l',axes=F,xlab="Stimulus",ylab="Accuracy",
        lty=1,ylim=c(0,1),lwd=2)
axis(1,at=1:2,lab=c("Darker Left","Darker Right"))
axis(2)
```

The overall accuracy was `r round(mean(m),2)`.  Figure \ref{fig:res} blah blah.

# Discussion

