---
title             : "Individual Differences in Congruency Effects"
shorttitle        : "My short title goes here"

author: 
  - name: Marcel Schreiner
    affiliation: "1"
    corresponding: yes    # Define only one corresponding author
    email: maschrei@mail.uni-mannheim.de
    address: Department of Research Methods and psychological Assessment, University of Mannheim
  - name: Theresa Koch
    affiliation: "1"
  - name: Nils Petras
    affiliation: "1"

affiliation       :
  - id: 1
    institution: University of Mannheim


author_note       : "This paper was written as part of an open science class"

abstract          : >
  "Here"
  
keywords          : "are just words"

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no


class             : "man"

output            : papaja::apa6_pdf
---

```{r include=FALSE}
library(lme4)
library(lmerTest)
library(tidyverse)
```

We investigated individual differences in visual inhibition.

# Method

We predicted performance by level of congruency. To do this, we estimated a multilevel model with random person intercepts and slopes for levels of congruency.

# Results

```{r loadData}
dat=read.csv(url('https://raw.githubusercontent.com/PerceptionCognitionLab/data3/master/brightCompare1/data'),header=TRUE)
```

```{r acc}
m=tapply(dat$correct,list(dat$targLevel,dat$backLevel),mean)
```

```{r wrangling, include=FALSE}
dat <- dat %>%
  mutate(condition = targLevel*backLevel)

moddat <- dat %>%
  group_by(pid, condition) %>%
  mutate(perf = mean(correct)) %>%
  distinct(pid, condition, .keep_all = TRUE) %>%
  arrange(pid, condition)
moddat$condition <- as.factor(moddat$condition)
```


```{r analysis, echo=FALSE}
mod0 <- lmer(correct ~ condition + (1 | pid), data = dat)
mod <- lmer(correct ~ condition + (1 + condition | pid), data = dat)
anova(mod0, mod, refit = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = moddat, mapping = aes(x = condition, y = perf, color = factor(pid))) +
  geom_point() +
  geom_smooth(aes(group = pid), method = "lm", se = FALSE) +
  geom_smooth(aes(group = 1), method = "lm", se = FALSE, color = "black", lwd = 2) +
  xlab("Congruency Condition") +
  ylab("Performance") +
  theme_bw() +
  theme(legend.position = "none")

```


The overall accuracy was `r round(mean(m),2)`.  Figure \ref{fig:res} blah blah.

# Discussion

There are individual differences in congruency effects.
